Summary of COVID-19 Cases in Toronto

### 2021-01-30 outputs/paper/paper.Rmd
Final Updates

\newpage
```{r line-1, fig.cap="line-1",warning=FALSE,message=FALSE, echo = FALSE, fig.width=8, fig.height=6}
data_2020<-
  COVID_data%>%
  filter(COVID_data$year == 2020)%>%
  group_by(month)%>%
  summarise(Total = n())

ggplot(data_2020, aes(x=month, y=Total))+
  geom_line( 
    color="red")+
  labs(x = "Months",
       y = "Number of Cases",
       title = "New Cases in Each Month in 2020")+
  scale_x_continuous(breaks= pretty_breaks())+
  theme(plot.title = element_text(hjust = 0.5),
      axis.text.x=element_text(margin = margin(1, unit = "cm"),siz=12,hjust = 0.5, vjust =1),
      title =element_text(size=20, face='bold'))
```

```{r bar-chart-1,fig.cap="bar-chart-1",warning=FALSE,message=FALSE,echo = FALSE, fig.width=10, fig.height=8}
COVID_data %>%
  ggplot(mapping = aes( x = `Age Group`, fill = `Client Gender`))+
  geom_bar()+
  theme_minimal()+
  labs(x = "Age Group",
       y = "Number of Cases",
       fill = "Patient Gender",
       title = "Number of Patient in Each Age Group")+
  theme(axis.text.x = element_text(angle = 90),
        title =element_text(size=20,hjust = 0.5)
        )
```

```{r bar-chart-2, fig.cap="bar-chart-2",warning=FALSE,message=FALSE,echo = FALSE, fig.width=25, fig.height=15}
COVID_data %>%
  ggplot(mapping = aes( x = FSA ))+
  geom_bar( fill = "dark blue")+
  theme_minimal()+
  labs(x = "Neighbourhood Name",
       y = "Number of cases",
       title = "Cases in Each Neighbourhood")+
  theme(axis.text.x=element_text(angle=90,margin = margin(1, unit = "cm"),siz=12,hjust = 0.5, vjust =1),
        title =element_text(size=40, face='bold'))

@@

COVID_sum_table%>%
  knitr::kable(caption = "Total Number of Three Outcomes", 
               col.names = c("Month", "Total Cases"),
               align = c('l', 'l', 'l'))
```

@@

COVID_table%>%
  knitr::kable(caption = "Outcomes of All Age Group",col.names = c("Outcome", "Age Group", "Total"))
```

>>>>

```{r line-1, fig.cap="line-1",warning=FALSE,message=FALSE, echo = FALSE, fig.width=8, fig.height=6}
data_2020<-
  COVID_data%>%
  filter(COVID_data$year == 2020)%>%
  group_by(month)%>%
  summarise(Total = n())

ggplot(data_2020, aes(x=month, y=Total))+
  geom_line( 
    color="red")+
  labs(x = "Months",
       y = "Number of Cases",
       title = "Number of New COVID-19 Cases in Toronto, by Months",
       subtitle ="New cases rised again from August, 2020")+
  scale_x_continuous(breaks= pretty_breaks())+
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
      axis.text.x=element_text(margin = margin(1, unit = "cm"),siz=12,hjust = 0.5, vjust =1),
      title =element_text(size=16, face='bold'))
```

```{r bar-chart-1,fig.cap="bar-chart-1",warning=FALSE,message=FALSE,echo = FALSE, fig.width=10, fig.height=8}
COVID_data %>%
  ggplot(mapping = aes( x = `Age Group`, fill = `Client Gender`))+
  geom_bar()+
  theme_minimal()+
  labs(x = "Age Group",
       y = "Number of Cases",
       fill = "Patient Gender",
       title = "Distribution of COVID-19 Cases by Age Group and Gender")+
  theme(axis.text.x = element_text(angle = 90),
        title =element_text(size=20,hjust = 0.5)
        )
```

```{r bar-chart-2, fig.cap="bar-chart-2",warning=FALSE,message=FALSE,echo = FALSE, fig.width=25, fig.height=15}
COVID_data %>%
  ggplot(mapping = aes( x = FSA ))+
  geom_bar( fill = "dark blue")+
  theme_minimal()+
  labs(x = "Neighbourhood Name",
       y = "Number of cases",
       title = "COVID-19 Cases in Each Neighbourhood")+
  theme(axis.text.x=element_text(angle=90,margin = margin(1, unit = "cm"),siz=12,hjust = 0.5, vjust =1),
        title =element_text(size=30, face='bold', hjust = 0.5),
        plot.title = element_text(size=40, face='bold', hjust = 0.5))

@@

COVID_sum_table%>%
  knitr::kable(caption = "Total Number of Three Outcomes", 
               col.names = c("Outcome", "Total Cases"),
               align = c('l', 'l', 'l'))
```

@@

COVID_table%>%
  knitr::kable(caption = "Possible Outcomes of All Age Group",col.names = c("Outcome", "Age Group", "Total"))
```
